---
title: "BA6 Project Proposal"
---

```{r setup, include=FALSE, echo = FALSE}
library("knitr")
```

```{r link, echo = FALSE}
link_markdown_Seattlegov <- paste0("[City of Seattle Open Data portal](", "https://dev.socrata.com/foundry/data.seattle.gov/y7pv-r3kh", ")")
```

### <span style="color:darkblue">Project Description</span>

#### General Information  

*Seattle Police Department Police Report Incident*, retrieved from `r link_markdown_Seattlegov`, is the dataset our group chose to work with. This dataset contains details about criminal incidents occurred within Seattle, and was recorded by responding officers’ initial police reports. The information was transmitted to data.seattle.gov after the incidents were filed into the system. The data we extracted for our group project consists *at least 1,000,000 rows from 1997 to 2018*.

#### Audience

For a crime report based on a particular area, almost everyone living within the area or whoever is interested in learning the safety issue of the area is likely to be concerned and find relevance. However, our group have decided to <span style="color:red">**focus on students near UW campus**</span>. In all, our goal in visualizing the chosen data is to provide our audience, namely the students, a better sense of their safety in Seattle.   

Hence, the specific questions our project will answer for our audience are as following:    

* What is the frequency of incidents based on types?    
* Is there any location that is particularly dangerous to go? what type of incident occurred the most in this given location?   
* When is the time that offenders are more likely to commit a crime? Daytime or Midnight? Will the situation vary if the type of crime is different?    
* Has the safety around UW campus declined or inclined?

### <span style="color:darkblue">Technical Description</span>
